\documentclass[a4paper, 11pt]{article}
\usepackage[margin=1in]{geometry} % full-width
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titling}
% \usepackage{tabto}
% \newcommand{\tablevelone}{\tabto{3in}}
\pretitle{
    \begin{center}
    \Huge\bfseries
}
\posttitle{
    \end{center}
    \noindent\vrule height 2pt width \textwidth
}
\usepackage[explicit]{titlesec}
\newcommand{\raisedrulefill}[2][0ex]{\leaders\hbox{\rule[#1]{0.1pt}{#2}}\hfill}
\titleformat{\section}{\Large\bfseries\MakeUppercase}{\thesection. }{0em}{#1\normalfont\,\raisedrulefill[0.7ex]{0.1pt}}

\title{Ezekiel Cochran\\Curriculum Vitæ}
\author{
    % Ezekiel Cochran \\
    16206 NE 36th Ave \\
    Ridgefield, WA 98642 \\
    (360) 768-7509 \\
    % \texttt{zeke.j.cochran@gmail.com} \\
    \texttt{ezekielcochran@letu.edu} \\
}
\date{}

\begin{document}
    \maketitle
        
    \section*{Education}\label{sec:education}
    \begin{itemize}
        \item B.S. Mathematics, pending 2024, LeTourneau University
        \item B.S. Computer Science (Math Concentration), pending 2024, LeTourneau University
        \item Minor in Physics, pending 2024, LeTourneau University
    \end{itemize}

    \section*{Research Interests}\label{sec:research_interests}
    \textit{Number Theory, Complex Analysis, Cybersecurity, Machine Learning.}
    My research interests encompass a diverse range of fields, and their practical applications.
    I am particularly intrigued by the intersection of the above topics in the context of new models of computing,
    and how they can enhance the security and efficiency of technological systems.
    Additionally, I am actively exploring the evolving role of machine learning in these domains
    and its potential to drive innovative solutions and advancements.
    
    \section*{Publications}\label{sec:publications}
    Cochran, E., Dawsey, M.L., Harrell, E. et al. \\
    Bijections, generalizations, and other properties of sequentially congruent partitions. \\
    Ramanujan J (2023). \url{https://doi.org/10.1007/s11139-023-00728-y}
    
    \section*{Academic Scores}\label{sec:academic_scores}
    \begin{tabbing}
        GPA \qquad\= 3.87 \\
        GRE \> 332 \\
        Putnam \> 10 \\
        SAT \> 1510 \\
    \end{tabbing}

    \section*{Principal Courses}\label{sec:principal_courses}
    \subsection*{Computer Science}\label{sec:cs_courses}
    \begin{itemize}
        \item COSC 2203 Data Structures
        \item COSC 3503 Operating Systems
        \item COSC 3603 Networks \& Data Communications
        \item COSC 3523 Analysis of Algorithms
        \item COSC 4603 Computer Theory
        \item COSC 4103 Computer Graphics
    \end{itemize}
    \subsection*{Mathematics}\label{sec:math_courses}
    \begin{itemize}
        \item MATH 4103 Real Analysis
        \item MATH 4963 Topology \hfill(pending spring 2024)
        \item MATH 3703 Abstract Algebra
        \item MATH 2303 Linear Algebra
        \item MATH 4403 Numerical Analysis \hfill(pending spring 2024)
        \item MATH 3903 History of Mathematics
        \item MATH 4953 Complex Analysis
        \item MATH 2203 Differential Equations
        \item MATH 3603 Mathematical Modeling
        \item MATH 2503 Logic, Sets, and Proofs
        \item MATH 3403 Statistics
        \item MATH 2023 Calculus 3
    \end{itemize}
    \subsection*{Physics}\label{sec:physics_courses}
    \begin{itemize}
        \item PHYS 3214 Relativity \& Quantum Theory
        \item PHYS 4953 Mathematical Methods in Physics
        \item PHYS 4253 Advanced Quantum Mechanics \hfill(pending spring 2024)
        \item PHYS 3951 Introduction to Research
    \end{itemize}
    
    \section*{Honors and Awards}\label{sec:awards}
    \begin{itemize}
        \item President of Kappa Zeta Chi
        \item LeTourneau Univeristy President's List
        \item ICPC - second place within division
        \item Commended National Merit Scholar
    \end{itemize}    
    
    \section*{Professional Experience}\label{sec:professional_experience}
    \subsection*{Collins Aerospace}
    \begin{itemize}
        \item \textbf{Software Engineer Intern} (Summer 2024) \\
        In the summer I will work with the cybersecurity group at Collins Aerospace,
        focusing on secure algorithms, and algorithms resistant to quantum computing attacks.
        This is a somewhat vague description becuase the work involves sensitive technologies and information.
    \end{itemize}
    \subsection*{LeTourneau University}
    \begin{itemize}
        \item \textbf{Resident Assistant} (2022 - 2024) \\
        I serve as the resident assistant for Kappa Zeta Chi, a society with an independant house at LeTourneau University.
        I am responsible for making sure the house is well taken care of,
        as well as serving as ex officio member of all committees, presiding over all executive meetings, authorizing all expenditures,
        and taking care of any necessary disciplinary action.
        \item \textbf{Math Lab Supervisor} (2022 - 2024)\\
        I tutor undergraduate students on a drop in basis during math lab, helping with any level of LeTourneau mathematics class.
    \end{itemize}
    \subsection*{UT Tyler}
    \begin{itemize}
        \item \textbf{Number Theory Researcher} (Summer 2022) \\
        I worked with a team of scholars at UT Tyler to explore, verify, and publish new results in number theory.
        % specifically sequentially congruent partitions.
        This was part of an NSF-funded REU.
    \end{itemize}
    \subsection*{Other Summer Jobs}
    \begin{itemize}
        \item \textbf{Farmhand} (Summers 2020, 2023) \\
        I worked at two different family farms over two summers, maintaining the property and working on odd projects.
        These included sanding and painting a barn, setting up a turn-down foundation, putting up fencing, and more,
        as well as taking care of the animals and other maintenence work.
        \item \textbf{CNC Machine Operator} (Summer 2021) \\
        I worked at Claude's Accurate Machining, operating and repairing CNC mills.
    \end{itemize}

    \section*{References}\label{sec:references}
    \noindent
    Cory Krause, Ph.D. \\
    Chair and Professor, Department of Mathematics \\
    LeTourneau University \\
    2100 South Mobberly Avenue \\
    Longview, TX 75602 \\
    \texttt{corykrause@letu.edu} \\
    (903) 233-3334 \\

    \noindent
    Madeline Dawsey, Ph.D. \\
    Assistant Professor, Department of Mathematics \\
    The University of Texas at Tyler \\
    3900 University Boulevard \\
    Tyler, TX 75799 \\
    \texttt{mdawsey@uttyler.edu} \\
    (903) 565-5839 \\

    \noindent
    Brent Baas, Ph.D. \\
    Chair and Professor, Department of Computer Science \\
    LeTourneau University \\
    2100 South Mobberly Avenue \\
    Longview, TX 75602 \\
    \texttt{brentbaas@letu.edu} \\
    (903) 233-3341 \\

    \noindent
    Glyn Gowing, Ph.D. \\
    Professor, Department of Computer Science \\
    LeTourneau University \\
    2100 South Mobberly Avenue \\
    Longview, TX 75602 \\
    \texttt{glyngowing@letu.edu} \\
    (903) 233-3343 \\
    
\end{document}
